Fast time-domain electromagnetic modelling in the frequency domain

### 2020-10-23 ManuscriptTime.tex
Add small note

\cite{GEO.08.Mulder} provide a computational complexity analysis of various
methods to model transient electromagnetic responses directly in the
time-domain, and compare it to the computation of transient EM responses in the
frequency-domain with a subsequent Fourier transform. They conclude the review
by stating \emph{\guillemotleft Although it remains to be seen which of the
four methods requires the least computer time for a given accuracy, the
frequency-domain approach appears to be attractive.\guillemotright} Their
approach is to minimize the computation time by having, in addition to the just
introduced adaptive gridding, an adaptive frequency selection scheme. This
scheme starts with computing the responses for a set of just five frequencies,
regularly sampled on a log-scale, from minimum to maximum required frequency.
All the other frequencies are interpolated with a shape-preserving
piecewise-cubic Hermite interpolation \citep[PCHIP, ][]{SIAM.80.Fritsch}.
Testing the stability of the obtained response by removing a single
frequency-value at a time their scheme decides if more frequencies in-between
the already computed ones are required. In this way frequencies are only added
if required, hence if certain criteria of response stability are not met. While
this method is good and effective for a single offset, it loses all its
advantages if one tries to compute different offsets within one computation, as
each offset requires a different set of adaptive frequencies. Additionally, it
hampers the parallelization over frequencies.

>>>>

\cite{GEO.08.Mulder} provide a computational complexity analysis of various
methods to model transient electromagnetic responses directly in the
time-domain, and compare it to the computation of transient EM responses in the
frequency-domain with a subsequent Fourier transform. They conclude the review
by stating \emph{\guillemotleft Although it remains to be seen which of the
four methods requires the least computer time for a given accuracy, the
frequency-domain approach appears to be attractive.\guillemotright} Their
\todo{mention the four methods}
approach is to minimize the computation time by having, in addition to the just
introduced adaptive gridding, an adaptive frequency selection scheme. This
scheme starts with computing the responses for a set of just five frequencies,
regularly sampled on a log-scale, from minimum to maximum required frequency.
All the other frequencies are interpolated with a shape-preserving
piecewise-cubic Hermite interpolation \citep[PCHIP, ][]{SIAM.80.Fritsch}.
Testing the stability of the obtained response by removing a single
frequency-value at a time their scheme decides if more frequencies in-between
the already computed ones are required. In this way frequencies are only added
if required, hence if certain criteria of response stability are not met. While
this method is good and effective for a single offset, it loses all its
advantages if one tries to compute different offsets within one computation, as
each offset requires a different set of adaptive frequencies. Additionally, it
hampers the parallelization over frequencies.
